Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-11-21 paper/search.tex
Correct the formula

This algorithm runs in time $\mathcal{O}(m^{k+1})$: There are at most $\sum_{i=0}{k}{m \choose i}=\mathcal{O}(m^k)$ different paths which must be followed. Following one path in the tree takes $\mathcal{O}(m)$ time. Therefore, the total time is $\mathcal{O}(m^{k+1})$ without the reporting of occurrences (which can be done in time linear to the number of occurrences).

>>>>

This algorithm runs in time $\mathcal{O}(m^{k+1})$: There are at most $\sum_{i=0}^{k}{m \choose i}=\mathcal{O}(m^k)$ different paths which must be followed. Following one path in the tree takes $\mathcal{O}(m)$ time. Therefore, the total time is $\mathcal{O}(m^{k+1})$ without the reporting of occurrences (which can be done in time linear to the number of occurrences).
